\vspace{-0.25em}\thetitle

### 2009-07-22 paper.tex
...

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[IETF 60]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[IETF 67]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[SIGCOMM 2004]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[UCSD]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traces.} 
\fig{svd}
\end{center}
\vspace{-0.85em}
\end{figure}

% The most direct way to demonstrate the motivating insight of this research is with pictures.

>>>>

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traces.} 
\fig{svd}
\end{center}
\vspace{-0.85em}
\end{figure}

Clearly visible in \Figure{svd} is linear structure:
points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling along subspaces of three or more dimensions appear as ``smears.''
